
\def\covmac{/Users/matiascovarrubias/Documents/universidad/NYU/Research/Repositories/marketsAI/marketsai/Documents/Figures}
\let\dir=\covmac

\documentclass[11pt,english]{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage[authoryear]{natbib}
\onehalfspacing

\makeatletter
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Textclass specific LaTeX commands.
\newlength{\lyxlabelwidth}      % auxiliary length 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% User specified LaTeX commands.
% Added by lyx2lyx
%  for proper underlining
\PassOptionsToPackage{normalem}{ulem}
\usepackage{ulem}
\let\cite@rig\cite
\newcommand{\b@xcite}[2][\%]{\def\def@pt{\%}\def\pas@pt{#1}
  \mbox{\ifx\def@pt\pas@pt\cite@rig{#2}\else\cite@rig[#1]{#2}\fi}}
\renewcommand{\underbar}[1]{{\let\cite\b@xcite\uline{#1}}}

\usepackage{tikz}
\usetikzlibrary{arrows,snakes,shapes,calc}
\usepackage{pgfplots}
\usepackage{color}
\definecolor{darkred}{rgb}{0.8,0.1,.3}

%\usepackage[pagebackref=true]{hyperref}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=blue,%
    filecolor=black,%
    anchorcolor=darkred,
    linkcolor=darkred,%
    urlcolor=cyan
}

\usepackage[titletoc,toc,title]{appendix}
\usepackage{colortbl}
\usepackage[bottom]{footmisc}
\usepackage{hhline}

% For auto-creation of tables
\usepackage{amsmath,amsthm, graphicx, setspace, booktabs, tabularx, subcaption}
\usepackage{amsfonts, fancyhdr, epstopdf, color, verbatim, pdflscape}
\usepackage[font=small,format=plain,labelfont=bf,textfont=it]{caption}
\usepackage{times}
\makeatother
\usepackage{babel}

% new commands
\newcommand{\E}{\mathbb{E}}

\begin{document}
\title{Deep Reinforcement Learning in Macroeconomic Models - Advance report}
\author{Matias Covarrubias}
\maketitle

Explain the state of the project. Announce new assistant. The advances I have made are:

\begin{itemize}
	\item Wrote introduction were Deep Reinforcement Learning is introduced as a "learning in macroeconomics" paper, following   Macet and Sargent and Evans and Hoppaholla. The new questions are bla. The reasons to present this are:  \medskip
	
	\item Formulated a simple version of the stochastic growth model with heterogenous agents, incomplete markets and aggregate risk in order to have a single guiding framework which exposes the main use cases of the technology. I manipulate this simple framework to calculate four experiments. \medskip
	
	\begin{enumerate}
		\item Planner formulation: \medskip
		\item Market formulation: \medskip
		\item Incomplete formulation. \medskip
		\item Fully AI based problem. \medskip
	\end{enumerate}

	\item 
\end{itemize}


\end{document}
